---
title: "TWD Praca domowa 4"
author: "Jakub Pingielski"
date: "8/11/2019"
output: html_document
---
    
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

library(tidyverse)
library(patchwork)

fullData <- read.csv("data.csv")

# Helper function
zeroOrOne <- function(x){ 
  if (x <0){return (0) }
  else(return(1))
  }

```

## 1 Original plot - red to blue
#### Aesthetically pleasing, nice choice of colors, but does it provide new insights into our data?

```{r plot}
plot1 <- ggplot(data = fullData, aes(x = reorder(firstWeekValues, -firstWeekNumbers), y = firstWeekNumbers)) + 
          geom_col(aes(fill = firstWeekNumbers), show.legend = FALSE) + 
          coord_flip() +
          theme_bw() + 
          geom_abline(intercept = 0, slope = 0, color = "white", size = 1) + 
          scale_fill_gradient2(low = "red", mid = "#262626", high = "#008fb3", midpoint = 0 ) + 
          theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"), # białe tło
                axis.line.x = element_blank(),  # usunięcie linii osi X
                axis.line.y = element_blank(), 
                axis.text = element_blank(), 
                axis.ticks = element_blank(),
                axis.title = element_blank(),
                plot.title = element_text(hjust = 0.5, face = 2)) +
          scale_y_continuous(breaks = seq(-2,2,0.4) ) + 
          ggtitle("S&P 500 SECTOR RETURNS")  + 
          geom_text(aes(y = -0.04 * sign(firstWeekNumbers), label = firstWeekValues), 
                position = position_dodge(width = 0.9), 
                size = 4 , angle = 0, color = "black", hjust = sapply(fullData$firstWeekNumbers, zeroOrOne))  + 
          geom_text(aes(y = firstWeekNumbers -0.1 * sign(firstWeekNumbers), label = firstWeekNumbers), 
                position = position_dodge(width = 0.9), 
                size = 4 , angle = 0, color = "white")

plot1
```

## 2 Black to (almost) white
#### Removing colors does not remove any information from the plot, shades of gray still represtents levels of intensity correctly. Drawback - almost white bars are harder to read on white background, color of labels should also be adjusted accordingly.

```{r plot2}

plot2 <- plot1 + scale_fill_gradient2(low = "black", mid = "gray40", high = "gray80", midpoint = 0 ) 

plot2
```

## 3 All gray
#### Removing gradient makes plot more clean and readable, all information is stil availalbe to the viewer.
```{r plot3}

plot3 <- plot1 + scale_fill_gradient2(low = "gray20", mid = "gray20", high = "gray20", midpoint = 0 ) 

plot3
```

## 4 Red to green 
#### Green is culturally connected with positive values and it may better suit this dataset.
```{r plot4}

plot4 <- plot1 + scale_fill_gradient2(low = "red", mid = "#262626", high = "green3", midpoint = 0 )

plot4
```


## 5 Viridis 
#### This color gradient is easier to read by people with colorblindness.
```{r plot5}
plot5 <- plot1 + scale_fill_gradient2(low = "#440154ff", mid = "#29AF7FFF", high = "#FDE725FF", midpoint = 0 )

plot5
```